\begin{rubric}{EMPLOYMENT HISTORY}

\entry*[Since Nov 24]%
    \textbf{Junior Monitoring and Evaluation Officer,} Associates in Research and Education for Development (ARED), Dakar, Senegal.
    
    Assisted in the implementation and supervision of the monitoring and evaluation system for ARED's programs and projects, particularly the Ndaw Wune program. Lead of the midline evaluation of Ndaw Wune. Collected and analyzed data, managed performance indicators, and produced activity reports. Developed and managed a database for tracking the Ndaw Wune program. Ensured the quality of collected data and monitored the effectiveness of activities. Contributed to sample design and the digitization of data collection tools. Assisted in identifying and designing key indicators for other components of the Gates Program. Produced weekly and monthly reports for activity monitoring.

\entry*[Nov 24-Feb 25]%
    \textbf{Research Assistant,} Centre for Economic and Social Research and Development (CRDES), Dakar, Senegal.
    
    Conducted a literature review and drafted a policy brief on women's empowerment in male-dominated labor sectors. Organized and facilitated stakeholder engagement meetings with partner organizations, including ASAFIN and CEDAF. Planned and supervised focus group discussions (FGDs) with female vocational students, families, and firms in male-dominated sectors. Drafted a final report summarizing key findings from stakeholder discussions and focus groups.

\entry*[May 24-Dec 24]%
    \textbf{Senior Research Officer,} National Agency for Statistics and Demography (ANSD), Dakar, Senegal.
    
    Research assistant for the second and the third phase of the Harmonised Survey of Household Living Conditions (``EHCVM-II''). Authored comprehensive poverty report, synthesizing data insights to inform national policies. Conducted in-depth analyses on the dynamics of poverty, on multidimensional poverty and the development of poverty maps to better understand regional disparities and target interventions. Preparation of the next phase of the poverty survey.

\entry*[Apr 24-May 24]%
    \textbf{Project Manager Assistant,} \textit{nLine}, Dakar \& Kaolack, Senegal.
    
    Assisted in managing the logistics and planning for data collection, improving the overall process efficiency. Trained and supervised data collectors, ensuring high-quality data entry. Monitored the data collection progress to ensure compliance with deadlines and quality standards.

\entry*[Jul 21-Oct 23]%
    \textbf{Junior Research Officer,} National Agency for Statistics and Demography (ANSD), Dakar, Senegal.
    
    Research assistant for the second phase of the Harmonised Survey of Household Living Conditions (``EHCVM-II''). Logistical management and planning of data collection. Training of data collectors, weekly reporting and drafting of monthly reports. Contributing to data cleansing and analysis for the national poverty report.

\entry*[Jan 23]%
    \textbf{Consultant,} Partnership for African Social and Governance Research (PASGR), Dakar, Senegal.
    
    Set up data collection application using Survey CTO for the survey "Young Women and Men's Aspirations and Resilience: Prospects for Livelihoods, Employment, and Accountability before, during and beyond COVID–19".

\entry*[Jul 22-Feb 23]%
    \textbf{Research assistant,} Centre for Economic and Social Research and Development (CRDES), Dakar, Senegal.
    
    Setting up data collection applications through survey CTO, monitoring the collection of various surveys, processing and clearing data, outputting and analysing results.

\entry*[Feb21-Jun 21]%
    \textbf{Research assistant,} Consortium for Economic and Social Research (CRES), Dakar, Senegal.
    
    Implementation of a carbon tax: ``Use of the Energy Balance and SAM to assess the level of $CO_{2}$ emissions from sectors and products''. Monitoring and data processing of the survey ``Resilience of the informal food economy to the test of COVID-19: What lessons can be learned from the experience of the large Dakar metropolis?''

\entry*[Dec 20-Feb 21]%
    \textbf{Junior Research Officer,} National Agency for Statistics and Demography (ANSD), Dakar, Senegal.
    
    Junior researcher: Assistance with the production of the data collection application, supervision of the data collection, data clearance and output of results for the "Benevolat" labour survey co-conducted with the ILO.

\entry*[Jul 20-Nov 20]%
    \textbf{Research assistant,} Institute for Research and Development (IRD), LPED, Dakar, Senegal.
    
    Production of wealth indicators by factorial methods, analysis of evolution \& study of the determining factors of poverty.
\end{rubric}